---
title: "Download_pressures"
author: "Caitie"
date: "08/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(doParallel)
library(foreach)
library(raster)
library(rgdal)
library(here)
```


# Pressures (stressors x vulnerability)

```{r}

#Pressure data rescaled by one time period 2013 can be found here:

#https://knb.ecoinformatics.org/view/doi:10.5063/F15718ZN


#Weblinks

pressure_urls<-c("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_artisanal_fishing_mol_20150714052300",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_demersal_destructive_fishing_mol_20150714052315",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_demersal_nondest_high_bycatch_mol_20150714052336",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_demersal_nondest_low_bycatch_mol_20150714052358",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_inorganic_mol_20150714052413",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_invasives_mol_20150714052418",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_night_lights_mol_20150714052420",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_ocean_acidification_mol_20150714052425",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_ocean_pollution_mol_20150714052438",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_oil_rigs_mol_20150714052446",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_pelagic_high_bycatch_mol_20150714052449",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_pelagic_low_bycatch_mol_20150714052502",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_plumes_fert_mol_20150714052515",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_plumes_pest_mol_20150714052522",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_population_mol_20150714052527",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_shipping_mol_20150714052539",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_slr_mol_20150714052551",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_sst_mol_20150714052619",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/pressure_one_2013_uv_mol_20150714052827",
                 "https://knb.ecoinformatics.org/knb/d1/mn/v2/object/cumulative_impact_one_2013_global_cumul_impact_2013_mol_20150714053146")
```


```{r}
cl<-makeCluster(7)
registerDoParallel(cl)

foreach(i = 1:length(pressure_urls)) %dopar% {
mydir<-here::here("raw_data/pressures") #path to save files
temp<-tempfile(tmpdir=mydir, fileext=".zip")
download.file(pressure_urls[i], temp)
unzip(temp, exdir=mydir)
unlink(temp) #delete the zip file
}
```

# All files

```{r}
mydir<-here("raw_data/pressures/")
files<-list.files(path = mydir, pattern = "combo.tif", full.names = T)
```

# Climate pressures

Here we calculate the cumulative impact from climate-based marine impacts. See Table S1 for justifactions.

```{r}
clim_press<-c(paste0(mydir,"slr_combo.tif"),
              paste0(mydir,"sst_combo.tif"),
              paste0(mydir,"uv_combo.tif"),
              paste0(mydir,"ocean_acidification_combo.tif"))


clim_stack<-stack(clim_press)

clim_sum<-sum(clim_stack)

writeRaster(clim_sum, here("output_data/pressures/climate_pressures_sum.tif"), overwrite = T)

```

# Land pressures

Here we calculate the cumulative impact from land-based marine impacts. See Table S1 for justifactions.

```{r}
land_press<-c(paste0(mydir,"inorganic_combo.tif"),
              paste0(mydir,"plumes_fert_combo.tif"),
              paste0(mydir,"plumes_pest_combo.tif"),
              paste0(mydir,"population_combo.tif"),
              paste0(mydir,"night_lights_combo.tif"))

land_stack<-stack(land_press)

land_sum<-sum(land_stack)

writeRaster(land_sum, here("output_data/pressures/land_pressures_sum.tif"), overwrite = T)

```

# Marine pressures

Here we calculate the cumulative impact from marine-based marine impacts. See Table S1 for justifactions.

```{r}
mar_press<-c(paste0(mydir,"artisanal_fishing_combo.tif"),
             paste0(mydir,"demersal_destructive_fishing_combo.tif"),
             paste0(mydir,"invasives_combo.tif"),
             paste0(mydir,"oil_rigs_combo.tif"),
             paste0(mydir,"pelagic_high_bycatch_combo.tif"),
             paste0(mydir,"shipping_combo.tif"),
             paste0(mydir,"ocean_pollution_combo.tif"),
             paste0(mydir,"pelagic_low_bycatch_combo.tif"),
             paste0(mydir,"demersal_nondest_high_bycatch_combo.tif"),
             paste0(mydir,"demersal_nondest_low_bycatch_combo.tif"))

mar_stack<-stack(mar_press)

mar_sum<-sum(mar_stack)

writeRaster(mar_sum, here("output_data/pressures/marine_pressures_sum.tif"), overwrite = T)
```

