---
title: "Reef_threats_plots"
author: "Caitie"
date: "09/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(sf)
library(raster)
library(reshape2)
library(countrycode)
library(RColorBrewer)
library(here)
library(ggrepel)
library(patchwork)
```

# Figures 1 and 2

Figures 1 and 2 were created outside of the R programming language, but can be recreated with the following data.

```{r}
iso3_reef_threats_shp<- st_read(here("output_data/reefs/iso3_reef_threats.shp")) %>% 
  mutate(prop_clim=clim_mean/cum_mean,
         prop_land = land_mean/cum_mean,
         prop_mar = mar_mean/cum_mean,
         test = prop_clim + prop_land + prop_mar)

reef_threats_shp<-st_read(here("output_data/reefs/reef_threats.shp")) %>% 
  mutate(prop_clim=clim_mean/cum_mean,
         prop_land = land_mean/cum_mean,
         prop_mar = mar_mean/cum_mean,
         test = prop_clim + prop_land + prop_mar)

iso3_reef_threats_df<- iso3_reef_threats_shp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

reef_threats_df<-reef_threats_shp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)
```

# Figure 3

Figure 3 can be recreated with the data below. Note additional editing was done outside of R to create the final figures in text.

Panel (A) Reef
```{r}
med_reef_land<-median(reef_threats_df$land_mean)
med_reef_mar<-median(reef_threats_df$mar_mean)

reef_plot<-ggplot(reef_threats_df, aes(x = land_mean, y = mar_mean, label = BCUID)) +
  geom_point() +
  theme_bw() + 
  geom_hline(yintercept = med_iso3_mar) +
  geom_vline(xintercept = med_iso3_land) +
  xlab("Average cumulative land impact") +
  ylab("Average cumulative marine impact") + 
  geom_text_repel() +
  xlim(0,1) +
  ylim(0,3)

reef_plot
```


Panel (B) Country
```{r}
med_iso3_land<-median(iso3_reef_threats_df$land_mean)
med_iso3_mar<-median(iso3_reef_threats_df$mar_mean)

iso3_plot<-ggplot(iso3_reef_threats_df, aes(x = land_mean, y = mar_mean, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() + 
  geom_hline(yintercept = med_iso3_mar) +
  geom_vline(xintercept = med_iso3_land) +
  xlab("Average cumulative land impact") +
  ylab("Average cumulative marine impact") + 
  geom_text_repel() +
  xlim(0,1.5) +
  ylim(0,5)

iso3_plot
```

```{r}
reef_plot/iso3_plot + plot_annotation(tag_levels = 'A')
```
```{r}
ggsave(here("figures/Figure3_land_vs_marine.png"), width = 13, height = 20, dpi = 300)

```

# Figure 4

```{r}
reef_diff<-st_read(here("output_data/results/reef_difference.shp"))
iso3_diff<-st_read(here("output_data/results/iso3_reef_difference.shp"))

reef_diff_df<- reef_diff %>% 
  as.data.frame() %>%
  dplyr::select(-geometry) 

reef_diff_df<- reef_diff_df%>% 
  mutate(ID = seq.int(nrow(reef_diff_df))) %>% 
  rename(cum_diff = cum_mean,
         land_diff = land_mean,
         clim_diff = clim_mean, 
         mar_diff = mar_mean)

iso3_diff_df<- iso3_diff %>% 
  as.data.frame() %>%
  dplyr::select(-geometry) %>% 
  rename(cum_diff = cum_mean,
         land_diff = land_mean,
         clim_diff = clim_mean, 
         mar_diff = mar_mean)


iso3_join<-full_join(iso3_reef_threats_df, iso3_diff_df, by = "ISO_Ter1")%>% 
  dplyr::select(ISO_Ter1, cum_mean, clim_mean, land_mean, mar_mean, cum_diff, clim_diff, land_diff, mar_diff)

reef_join<-full_join(reef_threats_df, reef_diff_df, by = "BCUID") %>% 
  dplyr::select(BCUID, cum_mean, clim_mean, land_mean, mar_mean, cum_diff, clim_diff, land_diff, mar_diff)

```


```{r}
med<-median(reef_join$clim_mean)
med_diff<-median(reef_join$clim_diff)

reef_clim_plot<-ggplot(reef_join, aes(x = clim_mean, y = clim_diff, label = BCUID)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,4) +
  ylim(0,1.25) +
  labs(title = "Climate")

reef_clim_plot
```

```{r}
med<-median(reef_join$mar_mean)
med_diff<-median(reef_join$mar_diff)

reef_mar_plot<-ggplot(reef_join, aes(x = mar_mean, y = mar_diff, label = BCUID)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,5) +
  ylim(-1, 0.04) +
  labs(title = "Marine")

reef_mar_plot
```

```{r}
med<-median(reef_join$land_mean)
med_diff<-median(reef_join$land_diff)

reef_land_plot<-ggplot(reef_join, aes(x = land_mean, y = land_diff, label = BCUID)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,1.6) +
  ylim(-0.075,0.075) +
  labs(title = "Land")

reef_land_plot
```

```{r}
med<-median(iso3_join$clim_mean)
med_diff<-median(iso3_join$clim_diff)

iso3_clim_plot<-ggplot(iso3_join, aes(x = clim_mean, y = clim_diff, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,4) +
  ylim(0,1.25) +
  labs(title = "Climate")

iso3_clim_plot
```

```{r}
med<-median(iso3_join$mar_mean)
med_diff<-median(iso3_join$mar_diff)

iso3_mar_plot<-ggplot(iso3_join, aes(x = mar_mean, y = mar_diff, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,5) +
  ylim(-1,0.04) +
  labs(title = "Marine")

iso3_mar_plot
```

```{r}
med<-median(iso3_join$land_mean)
med_diff<-median(iso3_join$land_diff)

iso3_land_plot<-ggplot(iso3_join, aes(x = land_mean, y = land_diff, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,1.6) +
  ylim(-0.075,0.075) +
  labs(title = "Land")

iso3_land_plot
```

```{r}
(reef_clim_plot + reef_mar_plot + reef_land_plot)/(iso3_clim_plot + iso3_mar_plot + iso3_land_plot) + plot_annotation(tag_levels = 'A')
```

```{r}
ggsave(here("figures/Figure4_impact_2013_vs_change.png"), width = 13, height = 13, dpi = 300)

```


# Supplementary Figure 2


```{r}
med<-median(reef_join$cum_mean)
med_diff<-median(reef_join$cum_diff)

reef_cum_plot<-ggplot(reef_join, aes(x = cum_mean, y = cum_diff, label = BCUID)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,10) +
  ylim(-0.5, 1.25) 

reef_cum_plot
```

```{r}
med<-median(iso3_join$cum_mean)
med_diff<-median(iso3_join$cum_diff)

iso3_cum_plot<-ggplot(iso3_join, aes(x = cum_mean, y = cum_diff, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = med_diff) +
  geom_vline(xintercept = med) +
  xlab("Cumulative impact (2013)") +
  ylab("Change in impact (2008-2013)") +
  geom_text_repel() +
  xlim(0,10) +
  ylim(-0.5,1.25) 

iso3_cum_plot
```

```{r}
reef_cum_plot/iso3_cum_plot + plot_annotation(tag_levels = "A")
```


```{r}
ggsave(here("figures/Supp_Figure2_cumulative_impact_2013_vs_change.png"), width = 13, height = 13, dpi = 300)

```

# Figure 5 

We will plot pressure vs. index for each cateogry with trend line and median pressure/median index in dotted lines.
Also will add some ISO3 names

```{r}
cons_index<-read.csv(here("output_data/results/Conservation_index_metric.csv")) %>% 
  filter(!iso3 == "MDG")
```

# Join data

```{r}
threat_cons<-full_join(iso3_reef_threats_df, cons_index, by = c("ISO_Ter1" = "iso3"))
```


## Climate

```{r}

median_climate_index<-median(threat_cons$climate, na.rm = T)
median_climate_stress<-median(threat_cons$clim_mean, na.rm = T)

clim_plot<-ggplot(threat_cons, aes(x = climate, y = clim_mean, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  labs(x = "", y = "Pressure") +
  geom_text_repel() +
  geom_hline(yintercept = median_climate_stress, linetype = "dashed") +
  geom_vline(xintercept = median_climate_index, linetype = "dashed") +
  geom_smooth(method = "lm") +
  ggtitle('Climate') +
  theme(plot.title = element_text(hjust = 0.5))

clim_plot
```

```{r}

median_marine_index<-median(threat_cons$marine, na.rm = T)
median_marine_stress<-median(threat_cons$mar_mean, na.rm = T)


mar_plot<-ggplot(threat_cons, aes(x = marine, y = mar_mean, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  labs(x = "Index", y = "") +
  geom_text_repel() +
  geom_hline(yintercept = median_marine_stress, linetype = "dashed") +
  geom_vline(xintercept = median_marine_index, linetype = "dashed") +
  geom_smooth(method = "lm")+
  ggtitle('Marine') +
  theme(plot.title = element_text(hjust = 0.5))

mar_plot
```

```{r}
median_land_index<-median(threat_cons$land, na.rm = T)
median_land_stress<-median(threat_cons$land_mean, na.rm = T)

land_plot<-ggplot(threat_cons, aes(x = land, y = land_mean, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  labs(x = "", y = "") +
  geom_text_repel() +
  geom_hline(yintercept = median_land_stress, linetype = "dashed") +
  geom_vline(xintercept = median_land_index, linetype = "dashed") +
  geom_smooth(method = "lm") +
  ggtitle('Land') +
  theme(plot.title = element_text(hjust = 0.5))

land_plot
```


```{r}
diff_threat_cons<-full_join(iso3_diff_df, cons_index, by = c("ISO_Ter1" = "iso3"))
```


```{r}
diff_median_climate_index<-median(diff_threat_cons$climate, na.rm = T)
diff_median_climate_stress<-median(diff_threat_cons$clim_diff, na.rm = T)

diff_clim_plot<-ggplot(diff_threat_cons, aes(x = climate, y = clim_diff, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  labs(x = "", y = "Change in pressure") +
  geom_text_repel() +
  geom_hline(yintercept = diff_median_climate_stress, linetype = "dashed") +
  geom_vline(xintercept = diff_median_climate_index, linetype = "dashed") +
  geom_smooth(method = "lm") +
  #ggtitle('Climate') +
  theme(plot.title = element_text(hjust = 0.5))

diff_clim_plot
```

```{r}
diff_median_marine_index<-median(diff_threat_cons$marine, na.rm = T)
diff_median_marine_stress<-median(diff_threat_cons$mar_diff, na.rm = T)


diff_mar_plot<-ggplot(diff_threat_cons, aes(x = marine, y = mar_diff, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  labs(x = "Index", y = "") +
  geom_text_repel() +
  geom_hline(yintercept = diff_median_marine_stress, linetype = "dashed") +
  geom_vline(xintercept = diff_median_marine_index, linetype = "dashed") +
  geom_smooth(method = "lm")+
  #ggtitle('Marine') +
  theme(plot.title = element_text(hjust = 0.5))

diff_mar_plot
```

```{r}
diff_median_land_index<-median(diff_threat_cons$land, na.rm = T)
diff_median_land_stress<-median(diff_threat_cons$land_diff, na.rm = T)

diff_land_plot<-ggplot(diff_threat_cons, aes(x = land, y = land_diff, label = ISO_Ter1)) +
  geom_point() +
  theme_bw() +
  labs(x = "", y = "") +
  geom_text_repel() +
  geom_hline(yintercept = diff_median_land_stress, linetype = "dashed") +
  geom_vline(xintercept = diff_median_land_index, linetype = "dashed") +
  geom_smooth(method = "lm") +
  #ggtitle('Land') +
  theme(plot.title = element_text(hjust = 0.5))

diff_land_plot
```

```{r}

patch<-clim_plot + mar_plot + land_plot + diff_clim_plot + diff_mar_plot + diff_land_plot +
  plot_annotation(tag_levels = 'A')

patch
```

```{r}
ggsave(here("figures/Figure5_Impact_Management_index.png"), width = 13, height = 8, dpi = 300)
```

# Supplementary Figure 3

```{r}
iso3_threats_long<-iso3_reef_threats_df %>% 
  pivot_longer(., cols = c("clim_mean", "land_mean", "mar_mean"), names_to = "cat_stress", values_to = "stress") %>% 
  mutate(cat_stress = ifelse(cat_stress == "clim_mean", "climate",
                             ifelse(cat_stress == "land_mean", "land",
                                    ifelse(cat_stress == "mar_mean", "marine", NA))))

cons_index_long<-cons_index %>% 
  pivot_longer(., cols = c("climate", "land", "marine"), names_to = "cat_stress", values_to = "cons_index")

threat_cons_long<-full_join(iso3_threats_long, cons_index_long, by = c("ISO_Ter1" = "iso3", "cat_stress"))
```


# Remove outliers

Pressure outliers

```{r}
pressure_outliers<-ggplot(threat_cons_long, aes(x=cat_stress, y=stress, color=cat_stress, label = ISO_Ter1)) +
  geom_boxplot()+
  stat_summary(
    aes(label = round(stat(y), 1)),
    geom = "text", 
    fun = function(y) { o <- boxplot.stats(y)$out; if(length(o) == 0) NA else o },
    hjust = -1
  ) +
  theme_bw() +
  labs(y = "Pressure", x = "Category")

# Singapore is outlier for marine and land

pressure_outliers

```

Outliers for index

```{r}
index_outliers<-ggplot(threat_cons_long, aes(x=cat_stress, y=cons_index, color=cat_stress, label = ISO_Ter1)) +
  geom_boxplot()+
  stat_summary(
    aes(label = round(stat(y), 2)),
    geom = "text", 
    fun.y = function(y) { o <- boxplot.stats(y)$out; if(length(o) == 0) NA else o },
    hjust = -1
  ) +
  theme_bw() +
  labs(y = "Index", x = "Category")

index_outliers

# Sri Lanka is an outlier on land
# Fiji, Solomon Islands and Bangladesh are outliers in climate

```
```{r}
pressure_outliers + index_outliers + plot_annotation(tag_levels = 'A')
```


```{r}
ggsave(here("figures/Supplementary_Figure3_Pressure_outliers.png"), dpi = 300)
```

