---
title: "Reef_threats"
author: "Caitie"
date: "08/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(sf)
library(tidyverse)
library(lwgeom)
library(here)
```


# Intersect country EEZs and reef shapefiles

## Country EEZ shapefile

Download data from https://www.marineregions.org/downloads.php

Dissolve country boundaries - FYI this takes awhile. Avoid running multiple times.

```{r}
eez<-st_read(here("raw_data/EEZ/eez_v10.shp"))

eez_moll<-st_transform(eez, "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs")

eez_moll<-st_make_valid(eez_moll)

#Dissolve by ISO_Ter1 variable

eez_moll_diss<-eez_moll %>% 
  group_by(ISO_Ter1) %>% 
  summarise()

st_write(eez_moll_diss, here("output_data/EEZ/eez_moll_diss.shp"), delete_layer = T)
```

## Reefs shapefile

```{r}
eez_moll_diss<-st_read(here("output_data/EEZ/eez_moll_diss.shp"))
eez_moll_diss<-st_make_valid(eez_moll_diss)
eez_moll_diss<-st_transform(eez_moll_diss, "+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs ")

reefs<-st_read(here("raw_data/reefs/50Reefs_Balanced.shp"))

reefs_moll<-st_transform(reefs, st_crs(eez_moll_diss))

reefs_moll<-st_make_valid(reefs_moll)
```

```{r}
eez_border<-eez_moll_diss %>% 
  mutate(id = 1) %>% 
  group_by(id) %>% 
  summarise(test = sum(id, na.rm = T))

st_write(eez_border, here("output_data/EEZ/eez_border.shp"), delete_layer = T)

eez_border<-st_read(here("output_data/EEZ/eez_border.shp"))
```


## Intersect

```{r}
iso3_reefs<-st_intersection(eez_moll_diss, reefs_moll)

#test<-st_cast(iso3_reefs, "POLYGON")

#Create new code for country/reef combos
st_write(iso3_reefs, here("output_data/reefs/eez_reefs_intersect.shp"), delete_layer = TRUE)
```


## Dissolve reefs within each country

```{r}
# Dissolve reefs within each country

reef_eez_moll_diss<-iso3_reefs %>% 
  group_by(ISO_Ter1) %>% 
  summarise()

st_write(reef_eez_moll_diss, here("output_data/reefs/eez_reefs_dissolve.shp"), delete_layer = T)

reef_eez_moll_diss<-st_read(here("output_data/reefs/eez_reefs_dissolve.shp"))

```

# Intersect EEZ with Reefs to remove land areas

```{r}
reefs_moll2<-st_intersection(reefs_moll, eez_border)

reefs_moll2<-reefs_moll2 %>% 
  dplyr::select(-id, -test) %>% 
  rename(BCUID = puid)

reefs_moll2_df<-reefs_moll2 %>% 
  mutate(area = st_area(.)) %>% 
  as.data.frame()%>% 
  dplyr::select(-geometry) 

st_write(reefs_moll2, here("output_data/reefs/Reefs_moll.shp"), delete.layer = T)

```

# Threat data

```{r}

# Cumulative

cum_sum<-raster(here("raw_data/pressures/global_cumul_impact_2013_all_layers.tif"))
  
# Land

land_sum<-raster(here("output_data/pressures/land_pressures_sum.tif"))

# Marine
  
mar_sum<-raster(here("output_data/pressures/marine_pressures_sum.tif"))

# Climate

clim_sum<-raster(here("output_data/pressures/climate_pressures_sum.tif"))
```


# Average 2013 cumulative pressures within reefs

Please note that the list elements are ordered, that is to say that the first list element corresponds to the first polygon. Because of this, any summary of the list will stay ordered with the polygon data.

```{r}
# Extract raster values to list object

reef_cum_vals <- raster::extract(cum_sum, reefs_moll2)
iso3_cum_vals<-raster::extract(cum_sum, reef_eez_moll_diss)

reef_cum_mean <-lapply(reef_cum_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_mean = ".")

iso3_cum_mean<-lapply(iso3_cum_vals, FUN=mean) %>% 
   unlist() %>% 
  as.data.frame() %>% 
  rename(cum_mean = ".")

```


# Average land/marine/climate cumulative pressures within reefs

```{r}
# Extract raster values to list object
reef_clim_vals <- raster::extract(clim_sum, reefs_moll2) 
reef_land_vals <- raster::extract(land_sum, reefs_moll2) 
reef_mar_vals <- raster::extract(mar_sum, reefs_moll2) 

iso3_clim_vals <- raster::extract(clim_sum, reef_eez_moll_diss)
iso3_land_vals <- raster::extract(land_sum,reef_eez_moll_diss)
iso3_mar_vals <- raster::extract(mar_sum, reef_eez_moll_diss)

# Use list apply to calculate mean for each polygon
reef_clim_mean<-lapply(reef_clim_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_mean = ".")

reef_land_mean<-lapply(reef_land_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_mean = ".")

reef_mar_mean<-lapply(reef_mar_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_mean = ".")

iso3_clim_mean<-lapply(iso3_clim_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_mean = ".")

iso3_land_mean<-lapply(iso3_land_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_mean = ".")

iso3_mar_mean<-lapply(iso3_mar_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_mean = ".")

```


# Join threat data to shapefiles

```{r}
reef_id<-reefs_moll2 %>% 
  as.data.frame() %>% 
  dplyr::select(BCUID) 

reef_threats<-cbind(reef_id,reef_cum_mean, reef_clim_mean, reef_land_mean, reef_mar_mean)

reef_threats_shp<-left_join(reefs_moll2, reef_threats, by = "BCUID") 

st_write(reef_threats_shp, here("output_data/reefs/reef_threats.shp"), delete_layer = T)

```

```{r}
iso3<-reef_eez_moll_diss %>% 
  as.data.frame() %>% 
  dplyr::select(ISO_Ter1)

iso3_reef_threats<-cbind(iso3,iso3_cum_mean, iso3_clim_mean, iso3_land_mean, iso3_mar_mean)

iso3_reef_threats_shp<-left_join(reef_eez_moll_diss, iso3_reef_threats, by = "ISO_Ter1")

st_write(iso3_reef_threats_shp, here("output_data/reefs/iso3_reef_threats.shp"), delete_layer = T)

```

# Change in cumulative impact

```{r}
change_cum_sum<-raster(here("output_data/pressure_difference/cum_diff.tif"))
  
# Land

change_land_sum<-raster(here("output_data/pressure_difference/land_pressures_diff.tif"))

# Marine
  
change_mar_sum<-raster(here("output_data/pressure_difference/mar_pressures_diff.tif"))

# Climate

change_clim_sum<-raster(here("output_data/pressure_difference/clim_pressures_diff.tif"))
```


```{r}
reef_cum_diff<- raster::extract(change_cum_sum, reefs_moll2)
reef_clim_diff <- raster::extract(change_clim_sum, reefs_moll2) 
reef_land_diff <- raster::extract(change_land_sum, reefs_moll2) 
reef_mar_diff <- raster::extract(change_mar_sum, reefs_moll2) 

iso3_cum_diff<-raster::extract(change_cum_sum, reef_eez_moll_diss)
iso3_clim_diff <- raster::extract(change_clim_sum, reef_eez_moll_diss)
iso3_land_diff <- raster::extract(change_land_sum,reef_eez_moll_diss)
iso3_mar_diff <- raster::extract(change_mar_sum, reef_eez_moll_diss)
```

```{r}
cum08<-raster(here("raw_data/pressure_difference/2008/global_cumul_impact_2008_all_layers_except_shipping_oceanpollution_invasives.tif"))
cum13<-raster(here("raw_data/pressure_difference/2013/global_cumul_impact_2013_all_layers_except_shipping_oceanpollution_invasives_slr.tif"))
```

```{r}
reef_cum_2008<-raster::extract(cum08, reefs_moll2)
reef_cum_2013<-raster::extract(cum13, reefs_moll2)
```

```{r}

reef_cum_mean_2008<-lapply(reef_cum_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_2008 = ".")

reef_cum_mean_2013<-lapply(reef_cum_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_2013 = ".")

cum_diff<-cbind(reef_cum_mean_2008, reef_cum_mean_2013) %>% 
  mutate(cum_diff = cum_2013 - cum_2008)
```


```{r}
clim_2008<-raster(here("output_data/pressure_difference/climate_pressures_sum_2008.tif"))
clim_2013<-raster(here("output_data/pressure_difference/climate_pressures_sum_2013.tif"))
```

```{r}
reef_clim_2008<-raster::extract(clim_2008, reefs_moll2)
reef_clim_2013<-raster::extract(clim_2013, reefs_moll2)
```

```{r}
reef_clim_mean_2008<-lapply(reef_clim_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_2008 = ".")

reef_clim_mean_2013<-lapply(reef_clim_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_2013 = ".")

climate_diff<-cbind(reef_clim_mean_2008, reef_clim_mean_2013) %>% 
  mutate(clim_diff = clim_2013 - clim_2008)
```

```{r}
mar_2008<-raster(here("output_data/pressure_difference/marine_pressures_sum_2008.tif"))
mar_2013<-raster(here("output_data/pressure_difference/marine_pressures_sum_2013.tif"))

```

```{r}
reef_mar_2008<-raster::extract(mar_2008, reefs_moll2)
reef_mar_2013<-raster::extract(mar_2013, reefs_moll2)
```


```{r}
reef_mar_mean_2008<-lapply(reef_mar_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_2008 = ".")

reef_mar_mean_2013<-lapply(reef_mar_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_2013 = ".")

mar_diff<-cbind(reef_mar_mean_2008, reef_mar_mean_2013) %>% 
  mutate(mar_diff = mar_2013 - mar_2008)
```


```{r}
land_2008<-raster(here("output_data/pressure_difference/land_pressures_sum_2008.tif"))
land_2013<-raster(here("output_data/pressure_difference/land_pressures_sum_2013.tif"))
```

```{r}
reef_land_2008<-raster::extract(land_2008, reefs_moll2)
reef_land_2013<-raster::extract(land_2013, reefs_moll2)
```


```{r}
reef_land_mean_2008<-lapply(reef_land_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_2008 = ".")

reef_land_mean_2013<-lapply(reef_land_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_2013 = ".")

land_diff<-cbind(reef_land_mean_2008, reef_land_mean_2013) %>% 
  mutate(land_diff = land_2013 - land_2008)
```

```{r}
reef_id<-reefs_moll2 %>% 
  as.data.frame() %>% 
  dplyr::select(BCUID)
```

```{r}
all_2008_2013<-cbind(reef_id, cum_diff, climate_diff, mar_diff, land_diff) %>% 
  filter(!BCUID == 30) %>% 
  mutate(prop_clim08 = clim_2008/cum_2008,
         prop_clim13 = clim_2013/cum_2013,
         prop_clim_diff = prop_clim13 - prop_clim08,
         prop_mar08 = mar_2008/cum_2008,
         prop_mar13 = mar_2013/cum_2013,
         prop_mar_diff = prop_mar13 - prop_mar08,
         prop_land08 = land_2008/cum_2008,
         prop_land13 = land_2013/cum_2013,
         prop_land_diff = prop_land13 - prop_land08)

write.csv(all_2008_2013, here("output_data/results/all_reef_2008_2013_diff.csv"))

```


```{r}
# Use list apply to calculate mean for each polygon
reef_cum_mean_diff<-lapply(reef_cum_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_mean = ".")

reef_clim_mean_diff<-lapply(reef_clim_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_mean = ".")

reef_land_mean_diff<-lapply(reef_land_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_mean = ".")

reef_mar_mean_diff<-lapply(reef_mar_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_mean = ".")

iso3_cum_mean_diff<-lapply(iso3_cum_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_mean = ".")

iso3_clim_mean_diff<-lapply(iso3_clim_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_mean = ".")

iso3_land_mean_diff<-lapply(iso3_land_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_mean = ".")

iso3_mar_mean_diff<-lapply(iso3_mar_diff, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_mean = ".")
```


```{r}
iso3_cum_2008<-raster::extract(cum08, reef_eez_moll_diss)
iso3_cum_2013<-raster::extract(cum13, reef_eez_moll_diss)
```

```{r}

iso3_cum_mean_2008<-lapply(iso3_cum_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_2008 = ".")

iso3_cum_mean_2013<-lapply(iso3_cum_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_2013 = ".")

iso3_cum_diff<-cbind(iso3_cum_mean_2008, iso3_cum_mean_2013) %>% 
  mutate(cum_diff = cum_2013 - cum_2008)
```



```{r}
iso3_clim_2008<-raster::extract(clim_2008, reef_eez_moll_diss)
iso3_clim_2013<-raster::extract(clim_2013,reef_eez_moll_diss)
```

```{r}
iso3_clim_mean_2008<-lapply(iso3_clim_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_2008 = ".")

iso3_clim_mean_2013<-lapply(iso3_clim_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_2013 = ".")

iso3_climate_diff<-cbind(iso3_clim_mean_2008, iso3_clim_mean_2013) %>% 
  mutate(clim_diff = clim_2013 - clim_2008)
```

```{r}
iso3_mar_2008<-raster::extract(mar_2008, reef_eez_moll_diss)
iso3_mar_2013<-raster::extract(mar_2013, reef_eez_moll_diss)
```


```{r}
iso3_mar_mean_2008<-lapply(iso3_mar_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_2008 = ".")

iso3_mar_mean_2013<-lapply(iso3_mar_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_2013 = ".")

iso3_mar_diff<-cbind(iso3_mar_mean_2008, iso3_mar_mean_2013) %>% 
  mutate(mar_diff = mar_2013 - mar_2008)
```


```{r}
iso3_land_2008<-raster::extract(land_2008, reef_eez_moll_diss)
iso3_land_2013<-raster::extract(land_2013, reef_eez_moll_diss)
```


```{r}
iso3_land_mean_2008<-lapply(iso3_land_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_2008 = ".")

iso3_land_mean_2013<-lapply(iso3_land_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_2013 = ".")

iso3_land_diff<-cbind(iso3_land_mean_2008, iso3_land_mean_2013) %>% 
  mutate(land_diff = land_2013 - land_2008)
```

```{r}
iso3<-reef_eez_moll_diss %>% 
  as.data.frame() %>% 
  dplyr::select(ISO_Ter1)
```

```{r}
iso3_all_2008_2013<-cbind(iso3, iso3_cum_diff, iso3_climate_diff, iso3_mar_diff, iso3_land_diff) %>% 
  filter(!ISO_Ter1 == "MDG") %>% 
  mutate(prop_clim08 = clim_2008/cum_2008,
         prop_clim13 = clim_2013/cum_2013,
         prop_clim_diff = prop_clim13 - prop_clim08,
         prop_mar08 = mar_2008/cum_2008,
         prop_mar13 = mar_2013/cum_2013,
         prop_mar_diff = prop_mar13 - prop_mar08,
         prop_land08 = land_2008/cum_2008,
         prop_land13 = land_2013/cum_2013,
         prop_land_diff = prop_land13 - prop_land08)

write.csv(iso3_all_2008_2013, here("output_data/results/all_iso3_2008_2013_diff.csv"))

```



```{r}

reef_threats_diff<-cbind(reef_id,reef_cum_mean_diff, reef_clim_mean_diff, reef_land_mean_diff, reef_mar_mean_diff)

reef_threats_diff_shp<-left_join(reefs_moll2, reef_threats_diff, by = "BCUID") 

st_write(reef_threats_diff_shp, here("output_data/results/reef_difference.shp"), delete_layer = T)
```


```{r}

iso3_reef_threats_diff<-cbind(iso3,iso3_cum_mean_diff, iso3_clim_mean_diff, iso3_land_mean_diff, iso3_mar_mean_diff)

iso3_reef_threats_diff_shp<-left_join(reef_eez_moll_diss, iso3_reef_threats_diff, by = "ISO_Ter1")

st_write(iso3_reef_threats_diff_shp, here("output_data/results/iso3_reef_difference.shp"), delete_layer = T)

```


