---
title: "Results"
author: "Caitie"
date: "13/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
library(countrycode)
```


# Load data

```{r}
iso3_reef_threats_shp<- st_read(here("output_data/reefs/iso3_reef_threats.shp")) %>% 
  mutate(prop_clim=clim_mean/cum_mean,
         prop_land = land_mean/cum_mean,
         prop_mar = mar_mean/cum_mean,
         test = prop_clim + prop_land + prop_mar,
         area_m2 =st_area(.),
         area_km2 = as.numeric(area_m2/1000000)) 

reef_threats_shp<-st_read(here("output_data/reefs/reef_threats.shp")) %>% 
  mutate(prop_clim=clim_mean/cum_mean,
         prop_land = land_mean/cum_mean,
         prop_mar = mar_mean/cum_mean,
         test = prop_clim + prop_land + prop_mar,
         area_m2 =st_area(.))

eez_reefs<-st_read(here("output_data/reefs/eez_reefs_intersect.shp")) %>% 
  rename(BCUID = puid)


```

Change to data frames

```{r}
reef_threats_df<-reef_threats_shp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  filter(!BCUID == 30)

iso3_threats_df<-iso3_reef_threats_shp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)  %>% 
  mutate(Country = countrycode(ISO_Ter1, "iso3c", "country.name")) %>% 
  filter(!ISO_Ter1 == "MDG")

eez_reef_df<- eez_reefs %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

eez_reef_threat_df<-full_join(eez_reef_df, reef_threats_df, by = "BCUID") %>% 
  mutate(Country = countrycode(ISO_Ter1, "iso3c", "country.name")) %>% 
  filter(!ISO_Ter1 == "MDG")

write_csv(iso3_threats_df, here("output_data/results/iso3_reef_threats_df.csv"))
write_csv(reef_threats_df, here("output_data/results/reef_threats_df.csv"))
write_csv(eez_reef_threat_df, here("output_data/results/eez_reef_threats_df.csv"))

```

# Reefs - Cumulative impacts


```{r}
min(reef_threats_df$cum_mean)
max(reef_threats_df$cum_mean)
mean(reef_threats_df$cum_mean)
```

```{r}
length(which(reef_threats_df$cum_mean >4))

length(which(reef_threats_df$cum_mean >4))/nrow(reef_threats_df)
```

```{r}
eez_reefs_df<-eez_reefs %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  filter(!BCUID == 30) %>% 
  group_by(ISO_Ter1) %>% 
  summarise(count = length(unique(BCUID)))

eez_reefs_df_bcu_count<-eez_reefs %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  filter(!BCUID == 30) %>% 
  group_by(BCUID) %>% 
  summarise(count = length(unique(ISO_Ter1)))

# Countries within each BCU
length(which(eez_reefs_df_bcu_count$count == 1))
length(which(eez_reefs_df_bcu_count$count == 2))
length(which(eez_reefs_df_bcu_count$count == 3))
length(which(eez_reefs_df_bcu_count$count >3))

# BCUs within each country
length(which(eez_reefs_df$count==1))
length(which(eez_reefs_df$count==2))
length(which(eez_reefs_df$count>2))
```

```{r}
View(reef_threats_df)
```


# Proportion climate impacts
```{r}
mean(reef_threats_df$prop_clim)
sd(reef_threats_df$prop_clim)
min(reef_threats_df$prop_clim)
max(reef_threats_df$prop_clim)

```


# Proportion land impacts
```{r}
mean(reef_threats_df$prop_land)
sd(reef_threats_df$prop_land)
min(reef_threats_df$prop_land)
max(reef_threats_df$prop_land)

```

# Proportion of marine impacts
```{r}
mean(reef_threats_df$prop_mar)
sd(reef_threats_df$prop_mar)
min(reef_threats_df$prop_mar)
max(reef_threats_df$prop_mar)

```


# Marine vs. land

```{r}
mar_med_reef<-median(reef_threats_df$mar_mean)
land_med_reef<-median(reef_threats_df$land_mean)

#Number of reefs with high marine and high land threats
length(which(reef_threats_df$mar_mean >= mar_med_reef & reef_threats_df$land_mean >= land_med_reef))

#Number of reefs with high marine and low land threats
length(which(reef_threats_df$mar_mean >= mar_med_reef & reef_threats_df$land_mean < land_med_reef))

length(which(reef_threats_df$mar_mean >= mar_med_reef & reef_threats_df$land_mean < land_med_reef))/nrow(reef_threats_df)
test<-reef_threats_df[which(reef_threats_df$mar_mean >= mar_med_reef & reef_threats_df$land_mean < land_med_reef),]

#Number of reefs with low marine and high land threats
length(which(reef_threats_df$mar_mean < mar_med_reef & reef_threats_df$land_mean >= land_med_reef))
length(which(reef_threats_df$mar_mean < mar_med_reef & reef_threats_df$land_mean >= land_med_reef))/nrow(reef_threats_df)
test<-reef_threats_df[which(reef_threats_df$mar_mean < mar_med_reef & reef_threats_df$land_mean >= land_med_reef),]

#Number of reefs with low marine and low land threats
length(which(reef_threats_df$mar_mean < mar_med_reef & reef_threats_df$land_mean < land_med_reef))
length(which(reef_threats_df$mar_mean < mar_med_reef & reef_threats_df$land_mean < land_med_reef))/nrow(reef_threats_df)
```


```{r}
# Number of BCUs within each country
n_c<-eez_reef_df %>% 
  filter(!BCUID == 30) %>% 
  group_by(ISO_Ter1) %>% 
  summarise(n = length(unique(BCUID)))

n_r<-eez_reef_df %>% 
  filter(!BCUID == 30) %>% 
  group_by(BCUID) %>% 
  summarise(n = length(unique(ISO_Ter1)))

length(which(n_c$n == 1))
length(which(n_r$n == 1))
length(which(n_r$n == 2))
length(which(n_r$n == 3))
length(which(n_r$n == 4))
```


# ISO3 - Cumulative impacts


```{r}
min(iso3_threats_df$cum_mean)
max(iso3_threats_df$cum_mean)
mean(iso3_threats_df$cum_mean)
sd(iso3_threats_df$cum_mean)
median(iso3_threats_df$cum_mean)
```

```{r}
length(which(iso3_threats_df$cum_mean >4))

length(which(iso3_threats_df$cum_mean >4))/nrow(iso3_threats_df)
```

# Proportion climate
```{r}
mean(iso3_threats_df$prop_clim)
sd(iso3_threats_df$prop_clim)
min(iso3_threats_df$prop_clim)
max(iso3_threats_df$prop_clim)

```

# Proportion land
```{r}
mean(iso3_threats_df$prop_land)
sd(iso3_threats_df$prop_land)
min(iso3_threats_df$prop_land)
max(iso3_threats_df$prop_land)

```

# Proportion marine
```{r}
mean(iso3_threats_df$prop_mar)
sd(iso3_threats_df$prop_mar)
min(iso3_threats_df$prop_mar)
max(iso3_threats_df$prop_mar)

```


# ISO3 Marine vs. land

```{r}
mar_med_iso3<-median(iso3_threats_df$mar_mean)
land_med_iso3<-median(iso3_threats_df$land_mean)

#Number of reefs with high marine and high land threats
length(which(iso3_threats_df$mar_mean >= mar_med_iso3 & iso3_threats_df$land_mean >= land_med_iso3))

test<-iso3_threats_df[which(iso3_threats_df$mar_mean >= mar_med_iso3 & iso3_threats_df$land_mean >= land_med_iso3),]

#Number of reefs with high marine and low land threats
length(which(iso3_threats_df$mar_mean >= mar_med_iso3 & iso3_threats_df$land_mean < land_med_iso3))
length(which(iso3_threats_df$mar_mean >= mar_med_iso3 & iso3_threats_df$land_mean < land_med_iso3))/nrow(iso3_threats_df)

test<-iso3_threats_df[which(iso3_threats_df$mar_mean >= mar_med_iso3 & iso3_threats_df$land_mean < land_med_iso3),]

#Number of reefs with low marine and high land threats
length(which(iso3_threats_df$mar_mean < mar_med_iso3 & iso3_threats_df$land_mean >= land_med_iso3))
length(which(iso3_threats_df$mar_mean < mar_med_iso3 & iso3_threats_df$land_mean >= land_med_iso3))/nrow(iso3_threats_df)

test<-iso3_threats_df[which(iso3_threats_df$mar_mean < mar_med_iso3 & iso3_threats_df$land_mean >= land_med_iso3),]

#Number of reefs with low marine and low land threats
length(which(iso3_threats_df$mar_mean < mar_med_iso3 & iso3_threats_df$land_mean < land_med_iso3))
length(which(iso3_threats_df$mar_mean < mar_med_iso3 & iso3_threats_df$land_mean < land_med_iso3))/nrow(iso3_threats_df)
```


```{r}
nc_df<-left_join(n_c, iso3_threats_df, by = "ISO_Ter1")

ggplot(nc_df, aes(x = cum_mean, y = n)) +
  geom_point()
```

# Correlation between impacts and number of BCUs in a country
```{r}
cor.test(nc_df$cum_mean, nc_df$n, method = "pearson")

nc_df2<-nc_df %>% 
  filter(!ISO_Ter1 %in% c("IDN", "AUS", "SGP"))

cor.test(nc_df2$cum_mean, nc_df2$n, method = "pearson")

```

```{r}
ggplot(nc_df2, aes(x = cum_mean, y = n)) +
  geom_point()
```

```{r}
nr_df<-left_join(n_r,reef_threats_df, by = "BCUID")

ggplot(nr_df, aes(x = cum_mean, y = n)) +
  geom_point()

```

```{r}
cor.test(nr_df$cum_mean, nr_df$n, method = "pearson")

```

# Change in cumulative impacts

```{r}
diff_iso3_threats_df<- read.csv(here("output_data/results/all_iso3_2008_2013_diff.csv")) %>% 
 dplyr::select(ISO_Ter1, cum_diff, clim_diff, mar_diff, land_diff, prop_clim_diff, prop_mar_diff, prop_land_diff) %>% 
  filter(!ISO_Ter1 == "MDG")  %>% 
  mutate(Country = countrycode(ISO_Ter1, "iso3c", "country.name"))

diff_reef_threats_df<-read.csv(here("output_data/results/all_reef_2008_2013_diff.csv")) %>% 
 dplyr::select(BCUID, cum_diff, clim_diff, mar_diff, land_diff, prop_clim_diff, prop_mar_diff, prop_land_diff) %>%
  filter(!BCUID == 30)
```


```{r}

diff_eez_reef_threat_df<-left_join(eez_reef_df, diff_reef_threats_df, by = "BCUID")

write_csv(diff_reef_threats_df, here("output_data/results/reef_difference_df.csv"))

write_csv(diff_iso3_threats_df, here("output_data/results/iso3_reef_difference_df.csv"))
```

```{r}
# How many BCUs increased threats

length(which(diff_reef_threats_df$cum_diff > 0))
length(which(diff_reef_threats_df$cum_diff > 0))/nrow(diff_reef_threats_df)
```

# Climate impacts

```{r}
length(which(diff_reef_threats_df$clim_diff > 0))
length(which(diff_reef_threats_df$clim_diff > 0))/nrow(diff_reef_threats_df)
mean(diff_reef_threats_df$clim_diff)
sd(diff_reef_threats_df$clim_diff)

```


# Land impacts
```{r}
length(which(diff_reef_threats_df$land_diff > 0))
length(which(diff_reef_threats_df$land_diff > 0))/nrow(diff_reef_threats_df)
mean(diff_reef_threats_df$land_diff)
sd(diff_reef_threats_df$land_diff)
```

# Marine impacts
```{r}
length(which(diff_reef_threats_df$mar_diff > 0))
length(which(diff_reef_threats_df$mar_diff > 0))/nrow(diff_reef_threats_df)
mean(diff_reef_threats_df$mar_diff)
sd(diff_reef_threats_df$mar_diff)
```

#Country results

```{r}
length(which(diff_iso3_threats_df$cum_diff > 0))
mean(diff_iso3_threats_df$cum_diff)
sd(diff_iso3_threats_df$cum_diff)

```
#climate

```{r}
length(which(diff_iso3_threats_df$clim_diff < 0))
mean(diff_iso3_threats_df$clim_diff)
sd(diff_iso3_threats_df$clim_diff)

```

#land

```{r}
length(which(diff_iso3_threats_df$land_diff < 0))
mean(diff_iso3_threats_df$land_diff)
sd(diff_iso3_threats_df$land_diff)

```

#marine
```{r}
length(which(diff_iso3_threats_df$mar_diff < 0))
mean(diff_iso3_threats_df$mar_diff)
sd(diff_iso3_threats_df$mar_diff)

```

# Comparing increases with 2013 threats

```{r}
diff_2013_reefs<-left_join(reef_threats_df, diff_reef_threats_df, by = "BCUID")

diff_2013_iso3<-left_join(iso3_threats_df, diff_iso3_threats_df, by = "ISO_Ter1")
```


```{r}
#Which reefs have a big increase and a high CHI in 2013

diff_med_reefs<-median(diff_2013_reefs$cum_mean)
diff_med_iso3<-median(diff_2013_iso3$cum_mean)

increase_reefs<-diff_2013_reefs[which(diff_2013_reefs$cum_diff > 0),] %>% 
  filter(cum_mean >=diff_med_reefs)

length(which(increase_reefs$land_diff>0 | increase_reefs$mar_diff >0))

increase_iso3<-diff_2013_iso3[which(diff_2013_iso3$cum_diff > 0),] %>% 
  filter(cum_mean >=diff_med_iso3)

test<-diff_2013_reefs[which(diff_2013_reefs$cum_mean>=diff_med_reefs & diff_2013_reefs$cum_diff> 0),]

land_test<-test[which(test$land_diff > 0),]

marine_test<-test[which(test$mar_diff > 0),] %>% 
  filter(!BCUID %in% land_test$BCUID)

increase_test<-rbind(land_test, marine_test) %>% 
  mutate(no_land_increase = land_mean - land_diff,
         no_mar_increase =  ifelse(mar_diff > 0, mar_mean - mar_diff, mar_mean),
         new_clim = clim_mean + clim_diff)

increase_test<-increase_test %>% 
  mutate(new_CHI = no_land_increase + no_mar_increase + new_clim,
         diff_CHI = cum_mean - new_CHI,
         prop_diff_CHI = diff_CHI/cum_mean)
```


# Management index

```{r}
cons_index<-read.csv(here("output_data/results/Conservation_index_metric.csv")) %>% 
  filter(!iso3 == "MDG")
```

# Join data

```{r}
threat_cons<-full_join(iso3_threats_df, cons_index, by = c("ISO_Ter1" = "iso3"))
```

```{r}
iso3_threats_long<-iso3_threats_df %>% 
  pivot_longer(., cols = c("clim_mean", "land_mean", "mar_mean"), names_to = "cat_stress", values_to = "stress") %>% 
  mutate(cat_stress = ifelse(cat_stress == "clim_mean", "climate",
                             ifelse(cat_stress == "land_mean", "land",
                                    ifelse(cat_stress == "mar_mean", "marine", NA))))

cons_index_long<-cons_index %>% 
  pivot_longer(., cols = c("climate", "land", "marine"), names_to = "cat_stress", values_to = "cons_index")

threat_cons_long<-full_join(iso3_threats_long, cons_index_long, by = c("ISO_Ter1" = "iso3", "cat_stress"))
```

# Climate threat vs. conservation potential


```{r}
cor.test(threat_cons$clim_mean, threat_cons$climate, method = "pearson")
```



# Land threat vs conservation potential

```{r}
cor.test(threat_cons$land_mean, threat_cons$land)
```



# Marine threat vs conservation potential

```{r}
cor.test(threat_cons$mar_mean, threat_cons$marine)
```

```{r}
cor.test(threat_cons$land, threat_cons$marine)
cor.test(threat_cons$climate, threat_cons$marine)
cor.test(threat_cons$land, threat_cons$climate)
```
 
 
```{r}
median_climate_index<-median(threat_cons$climate, na.rm = T)
median_climate_stress<-median(threat_cons$clim_mean, na.rm = T)

# High impacts low management
test<-threat_cons[which(threat_cons$clim_mean>=median_climate_stress & threat_cons$climate<median_climate_index),]

# High impacts high management
test<-threat_cons[which(threat_cons$clim_mean>=median_climate_stress & threat_cons$climate>=median_climate_index),]

# Low impacts, high management
test<-threat_cons[which(threat_cons$clim_mean<median_climate_stress & threat_cons$climate>=median_climate_index),]

# Low impacts, low management
threat_cons[which(threat_cons$clim_mean<median_climate_stress & threat_cons$climate<median_climate_index),]


```

```{r}
median_marine_index<-median(threat_cons$marine, na.rm = T)
median_marine_stress<-median(threat_cons$mar_mean, na.rm = T)

# High impacts high management
test<-threat_cons[which(threat_cons$mar_mean>=median_marine_stress & threat_cons$marine>=median_marine_index),]

# Low impacts, high management
test<-threat_cons[which(threat_cons$mar_mean<median_marine_stress & threat_cons$marine>=median_marine_index),]

# Low impacts, low management
test<-threat_cons[which(threat_cons$mar_mean<median_marine_stress & threat_cons$marine<median_marine_index),]

# High impacts low management
test<-threat_cons[which(threat_cons$mar_mean>=median_marine_stress & threat_cons$marine<median_marine_index),]

```

```{r}
median_land_index<-median(threat_cons$land, na.rm = T)
median_land_stress<-median(threat_cons$land_mean, na.rm = T)

# High impacts low management
test<-threat_cons[which(threat_cons$land_mean>=median_land_stress & threat_cons$land<median_land_index),]

# High impacts high management
test<-threat_cons[which(threat_cons$land_mean>=median_land_stress & threat_cons$land>=median_land_index),]

# Low impacts, high management
test<-threat_cons[which(threat_cons$land_mean<median_land_stress & threat_cons$land>=median_land_index),]

# Low impacts, low management
threat_cons[which(threat_cons$land_mean<median_land_stress & threat_cons$land<median_land_index),]

```
 
# Difference in threats vs. management index

```{r}
diff_threat_cons<-full_join(diff_iso3_threats_df, cons_index, by = c("ISO_Ter1" = "iso3"))
```


```{r}
cor.test(diff_threat_cons$clim_diff, diff_threat_cons$climate)
cor.test(diff_threat_cons$mar_diff, diff_threat_cons$marine)
cor.test(diff_threat_cons$land_diff, diff_threat_cons$land)
```

```{r}
diff_median_climate_index<-median(diff_threat_cons$climate, na.rm = T)
diff_median_climate_stress<-median(diff_threat_cons$clim_diff, na.rm = T)

# High change in impacts low management
test<-diff_threat_cons[which(diff_threat_cons$clim_diff>=diff_median_climate_stress & diff_threat_cons$climate<diff_median_climate_index),]

# High change in impacts high management
test<-diff_threat_cons[which(diff_threat_cons$clim_diff>=diff_median_climate_stress & diff_threat_cons$climate>=diff_median_climate_index),]

# High change in impacts high management
test<-diff_threat_cons[which(diff_threat_cons$clim_diff>=diff_median_climate_stress & diff_threat_cons$climate>=diff_median_climate_index),]


```

```{r}
diff_median_marine_index<-median(diff_threat_cons$marine, na.rm = T)
diff_median_marine_stress<-median(diff_threat_cons$mar_diff, na.rm = T)

# High change in impacts low management
test<-diff_threat_cons[which(diff_threat_cons$mar_diff>=diff_median_marine_stress & diff_threat_cons$marine<diff_median_marine_index),]

# High change in impacts high management
test<-diff_threat_cons[which(diff_threat_cons$mar_diff>=diff_median_marine_stress & diff_threat_cons$marine>=diff_median_marine_index),]

```

```{r}
diff_median_land_index<-median(diff_threat_cons$land, na.rm = T)
diff_median_land_stress<-median(diff_threat_cons$land_diff, na.rm = T)

# High impacts low management
test<-diff_threat_cons[which(diff_threat_cons$land_diff>=diff_median_land_stress & diff_threat_cons$land<diff_median_land_index),]

# High impacts high management
test<-diff_threat_cons[which(diff_threat_cons$land_diff>=diff_median_land_stress & diff_threat_cons$land>=diff_median_land_index),]
```

# Remove outliers

Pressure outliers

```{r}
pressure_outliers<-ggplot(threat_cons_long, aes(x=cat_stress, y=stress, color=cat_stress, label = ISO_Ter1)) +
  geom_boxplot()+
  stat_summary(
    aes(label = round(stat(y), 1)),
    geom = "text", 
    fun = function(y) { o <- boxplot.stats(y)$out; if(length(o) == 0) NA else o },
    hjust = -1
  ) +
  theme_bw() +
  labs(y = "Pressure", x = "Category")

# Singapore is outlier for marine and land

pressure_outliers

ggsave("/home/kuempel/Cumulative_threats_data/Figures/Pressure_outliers.png", dpi = 300)

```

Outliers for index

```{r}
index_outliers<-ggplot(threat_cons_long, aes(x=cat_stress, y=cons_index, color=cat_stress, label = ISO_Ter1)) +
  geom_boxplot()+
  stat_summary(
    aes(label = round(stat(y), 2)),
    geom = "text", 
    fun.y = function(y) { o <- boxplot.stats(y)$out; if(length(o) == 0) NA else o },
    hjust = -1
  ) +
  theme_bw() +
  labs(y = "Index", x = "Category")

index_outliers

# Sri Lanka is an outlier on land
# Fiji, Solomon Islands and Bangladesh are outliers in climate

ggsave("/home/kuempel/Cumulative_threats_data/Figures/Index_outliers.png", dpi = 300)
```

```{r}
sub_clim<-threat_cons %>% 
  filter(!ISO_Ter1 %in% c("FJI", "BGD"))

cor.test(sub_clim$climate, sub_clim$clim_mean, method = "pearson")
cor.test(threat_cons$climate, threat_cons$clim_mean, method = "pearson")

sub_land<-threat_cons %>% 
  filter(!ISO_Ter1 %in% c("SGP"))

cor.test(sub_land$land, sub_land$land_mean, method = "pearson")

sub_marine<-threat_cons %>% 
  filter(!ISO_Ter1 %in% c("SGP"))

cor.test(sub_marine$marine, sub_marine$mar_mean, method = "pearson")
```


# compare BCU and country

Look into Kenya and Somlia
```{r}
bcu_country<-full_join(reef_threats_df, eez_reef_df, by = "BCUID") %>% 
  full_join(iso3_threats_df, by = "ISO_Ter1")
```


# Calculate % decrease in CHI if cumulative land and marien threats were avoided between 2008 and 2013

```{r}
reef_all<-full_join(reef_threats_df, diff_reef_threats_df, by = "BCUID") %>% 
  mutate(cum_2013 = cum_mean + cum_diff,
         test_mar = ifelse(mar_diff >0, 0, as.numeric(mar_diff)),
         test_land = ifelse(land_diff>0, 0, as.numeric(land_diff)),
         test_cum_2013 = (clim_mean + clim_diff) + (land_mean + test_land) + (mar_mean + test_mar),
         perc_diff = (cum_2013 - test_cum_2013)/cum_2013)
```

