---
title: "Untitled"
author: "Caitie"
date: "23/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(sf)
library(tidyverse)
library(lwgeom)
library(countrycode)
library(here)
```

```{r}
#Country/reef intersect

iso3_reefs<-st_read(here("output_data/reefs/eez_reefs_intersect.shp"))
```

# 2013 threat data

```{r}

# Cumulative

cum_sum<-raster(here("raw_data/pressures/global_cumul_impact_2013_all_layers.tif"))
  
# Land

land_sum<-raster(here("output_data/pressures/land_pressures_sum.tif"))

# Marine
  
mar_sum<-raster(here("output_data/pressures/marine_pressures_sum.tif"))

# Climate

clim_sum<-raster(here("output_data/pressures/climate_pressures_sum.tif"))
```


# Average 2013 cumulative pressures within reefs

Please note that the list elements are ordered, that is to say that the first list element corresponds to the first polygon. Because of this, any summary of the list will stay ordered with the polygon data.

```{r}
# Extract raster values to list object

iso3_reef_cum_vals <- raster::extract(cum_sum, iso3_reefs)

# Use list apply to calculate mean for each polygon

iso3_reef_cum_mean<-lapply(iso3_reef_cum_vals, FUN=mean) %>% 
   unlist() %>% 
  as.data.frame() %>% 
  rename(cum_mean = ".")

```


# Average land/marine/climate cumulative pressures within reefs

```{r}
# Extract raster values to list object
iso3_reef_clim_vals <- raster::extract(clim_sum, iso3_reefs)
iso3_reef_land_vals <- raster::extract(land_sum,iso3_reefs)
iso3_reef_mar_vals <- raster::extract(mar_sum, iso3_reefs)

# Use list apply to calculate mean for each polygon
iso3_reef_clim_mean<-lapply(iso3_reef_clim_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_mean = ".")

iso3_reef_land_mean<-lapply(iso3_reef_land_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_mean = ".")

iso3_reef_mar_mean<-lapply(iso3_reef_mar_vals, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_mean = ".")

```


# Join threat data to shapefiles

```{r}
iso3<-iso3_reefs %>% 
  as.data.frame() %>% 
  rename(BCUID = puid) %>% 
  dplyr::select(ISO_Ter1, BCUID)

iso3_reef_threats<-cbind(iso3,iso3_reef_cum_mean, iso3_reef_clim_mean, iso3_reef_land_mean, iso3_reef_mar_mean)  %>% 
  mutate(prop_clim = clim_mean/cum_mean,
         prop_land = land_mean/cum_mean,
         prop_mar = mar_mean/cum_mean)

iso3_reef_threats_shp<-left_join(iso3_reefs, iso3_reef_threats, by = "ISO_Ter1")

st_write(iso3_reef_threats_shp, here("output_data/supplementary/Supp_reefs_by_iso3_threats.shp"), delete_layer = T)

```

# Change in cumulative impact

```{r}
cum08<-raster(here("raw_data/pressure_difference/2008/global_cumul_impact_2008_all_layers_except_shipping_oceanpollution_invasives.tif"))
cum13<-raster(here("raw_data/pressure_difference/2013/global_cumul_impact_2013_all_layers_except_shipping_oceanpollution_invasives_slr.tif"))

clim_2008<-raster(here("output_data/pressure_difference/climate_pressures_sum_2008.tif"))
clim_2013<-raster(here("output_data/pressure_difference/climate_pressures_sum_2013.tif"))

mar_2008<-raster(here("output_data/pressure_difference/marine_pressures_sum_2008.tif"))
mar_2013<-raster(here("output_data/pressure_difference/marine_pressures_sum_2013.tif"))

land_2008<-raster(here("output_data/pressure_difference/land_pressures_sum_2008.tif"))
land_2013<-raster(here("output_data/pressure_difference/land_pressures_sum_2013.tif"))
```



```{r}
iso3_reef_cum_08<-raster::extract(cum08, iso3_reefs)
iso3_reef_cum_13<-raster::extract(cum13, iso3_reefs)
iso3_reef_clim_2008 <- raster::extract(clim_2008, iso3_reefs)
iso3_reef_clim_2013<-raster::extract(clim_2013, iso3_reefs)
iso3_reef_land_2008 <- raster::extract(land_2008,iso3_reefs)
iso3_reef_land_2013 <- raster::extract(land_2013,iso3_reefs)
iso3_reef_mar_2008 <- raster::extract(mar_2008, iso3_reefs)
iso3_reef_mar_2013 <- raster::extract(mar_2013, iso3_reefs)
```


```{r}
# Use list apply to calculate mean for each polygon
iso3_reef_cum_2008<-lapply(iso3_reef_cum_08, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_2008 = ".")

iso3_reef_cum_2013<-lapply(iso3_reef_cum_13, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cum_2013 = ".")

iso3_reef_clim_mean_2008<-lapply(iso3_reef_clim_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_2008 = ".")

iso3_reef_clim_mean_2013<-lapply(iso3_reef_clim_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(clim_2013 = ".")

iso3_reef_land_mean_2008<-lapply(iso3_reef_land_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_2008 = ".")

iso3_reef_land_mean_2013<-lapply(iso3_reef_land_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(land_2013 = ".")

iso3_reef_mar_mean_2008<-lapply(iso3_reef_mar_2008, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_2008 = ".")

iso3_reef_mar_mean_2013<-lapply(iso3_reef_mar_2013, FUN=mean) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mar_2013 = ".")
```


```{r}
iso3<-iso3_reefs %>% 
  as.data.frame() %>% 
  rename(BCUID = puid) %>% 
  dplyr::select(ISO_Ter1, BCUID)

iso3_reef_threats_diff<-cbind(iso3,iso3_reef_cum_2008, iso3_reef_cum_2013, iso3_reef_clim_mean_2008,iso3_reef_clim_mean_2013, iso3_reef_land_mean_2008, iso3_reef_land_mean_2013, iso3_reef_mar_mean_2008, iso3_reef_mar_mean_2013) %>% 
  mutate(iso3_reef_cum_diff =  cum_2013 - cum_2008,
         iso3_reef_clim_diff = clim_2013 - clim_2008,
         iso3_reef_land_diff = land_2013 - land_2008,
         iso3_reef_mar_diff = mar_2013 - mar_2008)

iso3_reef_threats_diff_shp<-left_join(iso3_reefs, iso3_reef_threats_diff, by = "ISO_Ter1")

st_write(iso3_reef_threats_diff_shp, here("output_data/supplementary/Supp_reef_by_iso3_difference.shp"), delete_layer = T)

```



```{r}
iso3_reef_threats_diff2<-iso3_reef_threats_diff %>% 
  mutate(prop_clim08 = clim_2008/cum_2008,
         prop_clim13 = clim_2013/cum_2013,
         prop_clim_diff = prop_clim13 - prop_clim08,
         prop_mar08 = mar_2008/cum_2008,
         prop_mar13 = mar_2013/cum_2013,
         prop_mar_diff = prop_mar13 - prop_mar08,
         prop_land08 = land_2008/cum_2008,
         prop_land13 = land_2013/cum_2013,
         prop_land_diff = prop_land13 - prop_land08)

supp_table<-left_join(iso3_reef_threats, iso3_reef_threats_diff2, by = c("ISO_Ter1", "BCUID")) %>% 
  mutate(Country = countrycode(ISO_Ter1, "iso3c", "country.name"))

write_csv(supp_table, here("output_data/supplementary/Supp_reef_by_iso3_table.csv"))
```


